---
title: "Deplatforming Research Code"
output: pdf_document
date: "2024-01-09"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r setup, echo=FALSE}
#Reading data & libraries

library(ggplot2)
library(reshape2)
library(dplyr)
library(car)
library(matrixStats)

a <- read.csv("5111.csv")
guide <- read.csv("551.csv")

## variable label guide

#Q87_1 ---> ISIS sympathizers
#Q87_2 ---> Proud Boys
#Q87_3 ---> GLAAD
#Q87_6 ---> Planned Parenthood
#Q87_8 ---> Black Lives Matter
#Q87_9 ---> Focus on the family
#Q89   ---> People should be free to express their opinions, without fear of being harassed or punished by anyone
#Q91 (least) twitter
#Q92 (least) paypal
#Q93 (least) google
#Q94 (most)  twitter
#Q95 (most)  paypal
#Q96.1 (most) google


#Q7 gender
#Q5 age range
#Q9 education
#Q88 conservative/liberal
#Q11 party
#Q90 political activity
#Q13 ethnicity


#Q85 religion
#Q86 degree of religiousness


```




```{r}

#Combining 
a$least <- a$Q91 + a$Q92 + a$Q93
a$most <- a$Q94 + a$Q95 + a$Q96.1

a$merged <- (ifelse(is.na(a$least),0,a$least) + ifelse(is.na(a$most),0,a$most))/3
a$merged

a$ind <- ifelse(is.na(a$Q91), 0, 1)

mean(a$Q89[a$ind ==1])
mean(a$Q89[a$ind ==0])

t.test(a$Q89[a$ind ==1],a$Q89[a$ind ==0])

az <- a

az$least <- ifelse(is.na(az$least), 99, az$least)
az$most <- ifelse(is.na(az$most), 99, az$most)
az$Q91 <- ifelse(is.na(az$Q91), 99, az$Q91)
az$Q92 <- ifelse(is.na(az$Q92), 99, az$Q92)
az$Q93 <- ifelse(is.na(az$Q93), 99, az$Q93)
az$Q94 <- ifelse(is.na(az$Q94), 99, az$Q94)
az$Q95 <- ifelse(is.na(az$Q95), 99, az$Q95)
az$Q96.1 <- ifelse(is.na(az$Q96.1), 99, az$Q96.1)



d2 <- select(az,merged,ind,Q7,Q5,Q9,Q88,Q11,Q90_1,Q90_2,Q90_3,Q90_4,Q13,Q85,Q86,Q89,Q87_1,Q87_2,Q87_3,Q87_6,Q87_8,Q87_9,Q91,Q92, Q93,Q94,Q95,Q96.1,least,most)
d2 <- na.omit(d2)



az$least <- ifelse(is.na(az$least), 99, az$least)
az$most <- ifelse(is.na(az$most), 99, az$most)
az$Q91 <- ifelse(is.na(az$Q91), 99, az$Q91)
az$Q92 <- ifelse(is.na(az$Q92), 99, az$Q92)
az$Q93 <- ifelse(is.na(az$Q93), 99, az$Q93)
az$Q94 <- ifelse(is.na(az$Q94), 99, az$Q94)
az$Q95 <- ifelse(is.na(az$Q95), 99, az$Q95)
az$Q96.1 <- ifelse(is.na(az$Q96.1), 99, az$Q96.1)


d2[, 22:29][d2[, 22:29] == 99] <- NA

d2$merged2 <-((d2$merged-1)/(5-1))
d2$most2 <-((d2$most-1)/(5-1))
d2$least2 <-((d2$least-1)/(5-1))

d2$least <- d2$least/3
d2$most <- d2$most/3

#t.test(,a$Q96.1)

mean(d2$Q89)
mean(d2$most, na.rm = T)
mean(d2$least, na.rm = T)
mean(d2$Q91, na.rm = T)
mean(d2$Q92, na.rm = T)
mean(d2$Q93, na.rm = T)
mean(d2$Q94, na.rm = T)
mean(d2$Q95, na.rm = T)
mean(d2$Q96.1, na.rm = T)


t.test(d2$most,d2$least)
t.test(d2$most2,d2$least2)
t.test(d2$Q91,d2$Q94)
t.test(d2$Q92,d2$Q95)
t.test(d2$Q93,d2$Q96.1)

t.test(d2$Q93,d2$Q96.1)


#t.test(a$Q89,most/3)
#t.test(a$Q89,least/3)

a$ind <- ifelse(is.na(a$Q91), 0, 1)

mean(a$Q89[a$ind ==1])
mean(a$Q89[a$ind ==0])

t.test(a$Q89[a$ind ==1],a$Q89[a$ind ==0])


```


#regression model


```{r}
summary(lm(a$least~as.factor(a$Q5)+a$Q7+a$Q9+a$Q88+as.factor(a$Q11)+as.factor(a$Q13)+as.factor(a$Q85)+a$Q86+0))
summary(lm(a$most~as.factor(a$Q5)+a$Q7+a$Q9+a$Q88+as.factor(a$Q11)+as.factor(a$Q13)+as.factor(a$Q85)+a$Q86))
```

#plot by gender

```{r}

d <- select(a,merged,ind,Q7,Q5,Q9,Q88,Q11,Q90_1,Q90_2,Q90_3,Q90_4,Q13,Q85,Q86,Q89,Q87_1,Q87_2,Q87_3,Q87_6,Q87_8,Q87_9)
d <- na.omit(d)
d$ind <- as.factor(d$ind)
d$Q7 <- as.factor(d$Q7)
d$merged2 <-((d$merged-1)/(5-1))
gender <-  na.omit(select(d,merged2,ind,Q7))

gender <- gender %>%
 group_by(ind, Q7) %>%
  summarise(mean = mean(merged2),sd = sd(merged2))

gender_m <- gender[-4]
gender_s <- gender[-3]

#gender_m <- melt(gender_m)
#ggplot(gender, aes(ind, mean, fill = Q7)) + 
 # geom_bar(stat="identity", position = "dodge")

gender_m$sd <- gender_s$sd
gender_m$n <- as.integer(table(d$Q7,d$ind))

gender_m$label2 <- c("Most Liked", "Least Liked","Most Liked", "Least Liked")

pd = position_dodge(.2)    ### How much to jitter the points on the plot

ggplot(gender_m,                ### The data frame to use.
       aes(x     = ind,
           y     = mean,
           color = Q7)) +

    geom_point(shape = 15,
               size  = 4,
             position = pd) +

    geom_errorbar(aes(ymin  = mean - 1.96*(sd/sqrt(n)),
                      ymax  = mean + 1.96*(sd/sqrt(n))),
                      width = 0.2,
                      size  = 0.7,
                      position = pd) +
    theme_bw() +
    theme(axis.title = element_text(face = "bold")) +

    ylab("Mean Deplatforming Index Value") + xlab("Experimental Groups")  + ggtitle("Deplatforming Index Value between Experimental Groups by Gender") +
  theme(plot.title = element_text(hjust = 0.5),panel.background = element_rect(fill = 'beige'), axis.text.x =element_text(colour = "black", face = "bold"))+
  scale_x_discrete(labels =gender_m$label2) +  scale_color_manual(labels = c("Male", "Female"), values = c("blue","red"))+labs(color='Gender')

```



#Respondent Attitude Towards Social Media Deplatforming by Experimental Groups


```{r}


a$twitter_merged <- ifelse(is.na(a$Q91),0,a$Q91) + ifelse(is.na(a$Q94),0,a$Q94)
a$paypal_merged <- ifelse(is.na(a$Q92),0,a$Q92) + ifelse(is.na(a$Q95),0,a$Q95)
a$google_merged <- ifelse(is.na(a$Q93),0,a$Q93) + ifelse(is.na(a$Q96.1),0,a$Q96.1)

d <- select(a,merged,ind,Q7,Q5,Q9,Q88,Q11,Q90_1,Q90_2,Q90_3,Q90_4,Q13,Q85,Q86,Q89,Q87_1,Q87_2,Q87_3,Q87_6,Q87_8,Q87_9,twitter_merged,paypal_merged,google_merged)
d <- na.omit(d)

d$ind <- as.factor(d$ind)
d$twitter_merged <- as.factor(d$twitter_merged)
d$paypal_merged <- as.factor(d$paypal_merged)
d$google_merged <- as.factor(d$google_merged)


d$merged2 <-((d$merged-1)/(5-1))


twitter <-select(d,twitter_merged,ind)
twitter_1 <- twitter[twitter$ind ==1,][-2]
twitter_0 <-twitter[twitter$ind ==0,][-2]

twitter_1 <- summary(twitter_1$twitter_merged)/length(twitter_1$twitter_merged)*100
twitter_0 <- summary(twitter_0$twitter_merged)/length(twitter_0$twitter_merged)*100
value <- append(twitter_1,twitter_0)
twitter <- as.data.frame(value)
twitter$id <- as.factor(1:5)
twitter$ind <- as.factor(c(1,1,1,1,1,0,0,0,0,0))
#twitter$label <- as.factor(c(rep("Least Liked",5), rep("Most Liked",5)))
twitter$label2 <- as.factor(c("Most Liked", "Least Liked"))
twitter$Answer<-as.factor(c("Strongly disagree", "Somewhat Disagree","Neither agree nor disagree","Somewhat agree","Strongly Agree"))
twitter$Answer <- factor(twitter$Answer, levels =c("Strongly disagree", "Somewhat Disagree","Neither agree nor disagree","Somewhat agree","Strongly Agree") )


ggplot(twitter, aes(ind, value, fill = Answer, label = round(value,1))) + 
  geom_bar(stat="identity", position = "dodge") +
 geom_text(position=position_dodge(0.9), vjust=-0.4) + ylab("Percentage (%) of Respondents") + xlab("Respondent Answer") + ggtitle("Respondent Attitude Towards Social Media Deplatforming by Experimental Groups")+
  theme(plot.title = element_text(hjust = 0.5),panel.background = element_rect(fill = 'beige'), axis.text.x =element_text(colour = "black", face = "bold"))+
  scale_x_discrete(labels =twitter$label2)

#+
 # scale_color_manual(labels = c("Strongly disagree", "Somewhat Disagree","Neither agree nor disagree","Somewhat agree","Strongly Agree")) +guides(color=guide_legend("Answer"))
```


#Respondent Attitude Towards Financial Deplatforming by Experimental Groups

```{r}


a$twitter_merged <- ifelse(is.na(a$Q91),0,a$Q91) + ifelse(is.na(a$Q94),0,a$Q94)
a$paypal_merged <- ifelse(is.na(a$Q92),0,a$Q92) + ifelse(is.na(a$Q95),0,a$Q95)
a$google_merged <- ifelse(is.na(a$Q93),0,a$Q93) + ifelse(is.na(a$Q96.1),0,a$Q96.1)

d <- select(a,merged,ind,Q7,Q5,Q9,Q88,Q11,Q90_1,Q90_2,Q90_3,Q90_4,Q13,Q85,Q86,Q89,Q87_1,Q87_2,Q87_3,Q87_6,Q87_8,Q87_9,twitter_merged,paypal_merged,google_merged)
d <- na.omit(d)

d$ind <- as.factor(d$ind)
d$twitter_merged <- as.factor(d$twitter_merged)
d$paypal_merged <- as.factor(d$paypal_merged)
d$google_merged <- as.factor(d$google_merged)


d$merged2 <-((d$merged-1)/(5-1))


paypal <-select(d,paypal_merged,ind)
paypal_1 <- paypal[paypal$ind ==1,][-2]
paypal_0 <-paypal[paypal$ind ==0,][-2]

paypal_1 <- summary(paypal_1$paypal_merged)/length(paypal_1$paypal_merged)*100
paypal_0 <- summary(paypal_0$paypal_merged)/length(paypal_0$paypal_merged)*100
value <- append(paypal_1,paypal_0)
paypal <- as.data.frame(value)
paypal$id <- as.factor(1:5)
paypal$ind <- as.factor(c(1,1,1,1,1,0,0,0,0,0))
paypal$label <- as.factor(c(rep("Least Liked",5), rep("Most Liked",5)))
paypal$label2 <- as.factor(c("Most Liked", "Least Liked"))
paypal$Answer<-as.factor(c("Strongly disagree", "Somewhat Disagree","Neither agree nor disagree","Somewhat agree","Strongly Agree"))
paypal$Answer <- factor(paypal$Answer, levels =c("Strongly disagree", "Somewhat Disagree","Neither agree nor disagree","Somewhat agree","Strongly Agree") )




ggplot(paypal, aes(ind, value, fill = Answer,label = round(value,1))) + 
  geom_bar(stat="identity", position = "dodge") +
 geom_text(position=position_dodge(0.9), vjust=-0.6)+
  scale_x_discrete(labels =paypal$label2) + ylab("Percentage (%) of Respondents") + xlab("Respondent Answer by Group") + ggtitle("Respondent Attitude Towards Financial Deplatforming by Experimental Groups")+
  theme(plot.title = element_text(hjust = 0.5),panel.background = element_rect(fill = 'beige'), axis.text.x =element_text(colour = "black", face = "bold"))
```


#Respondent Attitude Towards Application/Platform Deplatforming by Experimental Groups

```{r}
a$twitter_merged <- ifelse(is.na(a$Q91),0,a$Q91) + ifelse(is.na(a$Q94),0,a$Q94)
a$paypal_merged <- ifelse(is.na(a$Q92),0,a$Q92) + ifelse(is.na(a$Q95),0,a$Q95)
a$google_merged <- ifelse(is.na(a$Q93),0,a$Q93) + ifelse(is.na(a$Q96.1),0,a$Q96.1)

d <- select(a,merged,ind,Q7,Q5,Q9,Q88,Q11,Q90_1,Q90_2,Q90_3,Q90_4,Q13,Q85,Q86,Q89,Q87_1,Q87_2,Q87_3,Q87_6,Q87_8,Q87_9,twitter_merged,paypal_merged,google_merged)
d <- na.omit(d)

d$ind <- as.factor(d$ind)
d$twitter_merged <- as.factor(d$twitter_merged)
d$paypal_merged <- as.factor(d$paypal_merged)
d$google_merged <- as.factor(d$google_merged)


d$merged2 <-((d$merged-1)/(5-1))


google <-select(d,google_merged,ind)
google_1 <- google[google$ind ==1,][-2]
google_0 <-google[google$ind ==0,][-2]

google_1 <- summary(google_1$google_merged)/length(google_1$google_merged)*100
google_0 <- summary(google_0$google_merged)/length(google_0$google_merged)*100
value <- append(google_1,google_0)
google <- as.data.frame(value)
google$id <- as.factor(1:5)
google$ind <- as.factor(c(1,1,1,1,1,0,0,0,0,0))
google$label <- as.factor(c(rep("Most Liked",5), rep("Least Liked",5)))
google$label2 <- as.factor(c("Least Liked", "Most Liked"))
google$Answer<-as.factor(c("Strongly disagree", "Somewhat Disagree","Neither agree nor disagree","Somewhat agree","Strongly Agree"))
google$Answer <- factor(google$Answer, levels =c("Strongly disagree", "Somewhat Disagree","Neither agree nor disagree","Somewhat agree","Strongly Agree") )





  ggplot(google, aes(ind, value, fill = Answer,label = round(value,1))) + 
  geom_bar(stat="identity", position = "dodge")+
 geom_text(position=position_dodge(0.9), vjust=-0.6)+
  scale_x_discrete(labels =google$label2)+ ylab("Percentage (%) of Respondents") + xlab("Respondent Answer") + ggtitle("Respondent Attitude Towards Application/Platform Deplatforming by Experimental Groups")+
  theme(plot.title = element_text(hjust = 0.5),panel.background = element_rect(fill = 'beige'), axis.text.x =element_text(colour = "black", face = "bold"))

```

#Mean Value for Dimensions of Deplatforming in Least Liked Group

```{r}
library(matrixStats)
index <-  select(d,merged2,ind)

index <- index %>%
 group_by(ind) %>%
  summarise(mean = mean(merged2),sd = sd(merged2))

index_m <- index[-3]
index_s <- index[-2]
index_m$sd <- index_s$sd
index_m$n <- c(353,335)

index_m$label <- c("Most Liked", "Least Liked")
index_m$label  <- factor(index_m$label, levels =c("Most Liked", "Least Liked") )
#long$variable <- car::recode(long$variable,"c('Q87_1') = 'ISIS Sympathizers';c('Q87_2') = 'Proud Boys';c('Q87_3') = 'GLAAD';c('Q87_6') = 'Planned Parenthood';c('Q87_8') = 'Black Lives Matter';c('Q87_9') = 'Focus on the family'") 

pd = position_dodge(.2)    ### How much to jitter the points on the plot

ggplot(index_m ,                ### The data frame to use.
       aes(x     = label,
           y     = mean)) +

    geom_point(shape = 15,
               size  = 4,
             position = pd) +

    geom_errorbar(aes(ymin  = mean - 1.96*(sd/sqrt(n)),
                      ymax  = mean + 1.96*(sd/sqrt(n))),
                      width = 0.2,
                      size  = 0.7,
                      position = pd) +
    theme_bw() +
    theme(axis.title = element_text(face = "bold"),plot.title = element_text(hjust = 0.5), axis.text.x =element_text(colour = "black", face = "bold")) +

     

    ylab("Mean Deplatforming Index Value") + xlab("Experiment Group") + 
  
    ggtitle(" Mean Value for Dimensions of Deplatforming in Least Liked Group")



library("phenesse")
mean(d$merged2[d$ind==1&d$Q7==1]) +(1.96)*((sd(d$merged2[d$ind==1&d$Q7==1]))/sqrt(length(d$merged2[d$ind==1&d$Q7==1])))
mean_ci(d$merged2[d$ind==1&d$Q7==2])
```

#People should be free to express their opinions, without fear of being harassed or punished by anyone

```{r}
library(RColorBrewer)
library(tidyverse)
d$Q89<- as.factor(d$Q89)

m <- (summary(d$Q89))
v<- as.data.frame(m)
v$x <- as.factor(1:5)
v$label <-as.factor(c("Strongly disagree", "Somewhat Disagree","Neither agree nor disagree","Somewhat agree","Strongly Agree"))

a22 <- select(a,merged,ind,Q7,Q5,Q9,Q88,Q11,Q90_1,Q90_2,Q90_3,Q90_4,Q13,Q85,Q86,Q89,Q87_1,Q87_2,Q87_3,Q87_6,Q87_8,Q87_9)
a22 <- na.omit(a22)
a22 <- na.omit(select(a22,Q89))

ggplot(v,aes(x,(m/688)*100))+ geom_bar(stat="identity", color = "orange",fill = "blue", width = 0.5) +
  scale_x_discrete(labels =v$label, guide = guide_axis(n.dodge = 2))+ ylab("Percentage (%) of Respondents") + xlab("Respondent Answer") + ggtitle("People should be free to express their opinions,
 without fear of being harassed or punished by anyone")+
  theme(plot.title = element_text(hjust = 0.5),panel.background = element_rect(fill = 'beige'), axis.text.x =element_text(colour = "black", face = "bold"))

```

#age

```{r}


d <- select(a,merged,ind,Q7,Q5,Q9,Q88,Q11,Q90_1,Q90_2,Q90_3,Q90_4,Q13,Q85,Q86,Q89,Q87_1,Q87_2,Q87_3,Q87_6,Q87_8,Q87_9)
d <- na.omit(d)

d <- d[d$Q5 != 1, ]
d <- d[d$Q5 != 8, ]

d$ind <- as.factor(d$ind)
d$Q5 <- as.factor(d$Q5)
d$merged2 <-((d$merged-1)/(5-1))
age <-  na.omit(select(d,merged2,ind,Q5))

age <- age %>%
 group_by(ind, Q5) %>%
  summarise(mean = mean(merged2),sd = sd(merged2))

age_m <- age[-4]
age_s <- age[-3]

#age_m <- melt(age_m)
#ggplot(age, aes(ind, mean, fill = Q5)) + 
 # geom_bar(stat="identity", position = "dodge")

age_m$sd <- age_s$sd
age_m$n <- as.integer(na.omit(ifelse(as.integer(table(d$Q5,d$ind)) == 0, NA,as.integer(table(d$Q5,d$ind)))))

age_m$label2 <- c("Most Liked", rep("Least Liked",(length(age_m$mean)-1)))

age_m$Age <- as.factor(rep(c("18 – 24","25 – 34", "35 – 44","45 – 54","55 – 64","65 – 74"),2))

age_m$Age <- factor(age_m$Age, levels =c("18 – 24","25 – 34", "35 – 44","45 – 54","55 – 64","65 – 74") )

pd = position_dodge(.9)    ### How much to jitter the points on the plot

ggplot(age_m,                ### The data frame to use.
       aes(x     = ind,
           y     = mean,
           fill= Age)) + 
  geom_bar(stat="identity", position = "dodge")  +

    geom_errorbar(aes(ymin  = mean - 1.96*(sd/sqrt(n)),
                      ymax  = mean + 1.96*(sd/sqrt(n))),
                         size=.5,  
                width=.2,
                      position = pd) +
    

    ylab("Mean Deplatforming Index Value") + xlab("Experimental Groups")  + ggtitle("Deplatforming Index Value between Experimental Groups by Age") +
  theme(plot.title = element_text(hjust = 0.5),panel.background = element_rect(fill = 'beige'), axis.text.x =element_text(colour = "black", face = "bold"))+
  scale_x_discrete(labels =age_m$label2) +  scale_color_manual(labels = c("18 – 24","25 – 34", "35 – 44","45 – 54","55 – 64","65 – 74"), values = c("red","green","blue","cyan","magenta","brown"))+labs(color='Age Groups')+ scale_y_continuous(breaks=seq(0,1,0.1))






```

#education


```{r}




d <- select(a,merged,ind,Q7,Q5,Q9,Q88,Q11,Q90_1,Q90_2,Q90_3,Q90_4,Q13,Q85,Q86,Q89,Q87_1,Q87_2,Q87_3,Q87_6,Q87_8,Q87_9)
d <- na.omit(d)

d <- d[d$Q9 != 1, ]


d$ind <- as.factor(d$ind)
d$Q9 <- as.factor(d$Q9)
d$merged2 <-((d$merged-1)/(5-1))
education <-  na.omit(select(d,merged2,ind,Q9))

education <- education %>%
 group_by(ind, Q9) %>%
  summarise(mean = mean(merged2),sd = sd(merged2))

education_m <- education[-4]
education_s <- education[-3]

#education_m <- melt(education_m)
#ggplot(education, aes(ind, mean, fill = Q9)) + 
 # geom_bar(stat="identity", position = "dodge")

education_m$sd <- education_s$sd
education_m$n <- as.integer(na.omit(ifelse(as.integer(table(d$Q9,d$ind)) == 0, NA,as.integer(table(d$Q9,d$ind)))))

education_m$label2 <- c("Most Liked", rep("Least Liked",(length(education_m$mean)-1)))

education_m$Education <- as.factor(rep(c("High school graduate","Some college
", "2-year degree","4-year degree","Professional degree","Doctorate"),2))

education_m$Education <- factor(education_m$Education, levels =c("High school graduate","Some college
", "2-year degree","4-year degree","Professional degree","Doctorate") )

pd = position_dodge(.9)    ### How much to jitter the points on the plot

ggplot(education_m,                ### The data frame to use.
       aes(x     = ind,
           y     = mean,
           fill= Education)) + 
  geom_bar(stat="identity", position = "dodge")  +

    geom_errorbar(aes(ymin  = mean - 1.96*(sd/sqrt(n)),
                      ymax  = mean + 1.96*(sd/sqrt(n))),
                         size=.5,  
                width=.2,
                      position = pd) +
    

    ylab("Mean Deplatforming Index Value") + xlab("Experimental Groups")  + ggtitle("Deplatforming Index Value between Experimental Groups by education") +
  theme(plot.title = element_text(hjust = 0.5),panel.background = element_rect(fill = 'beige'), axis.text.x =element_text(colour = "black", face = "bold"))+
  scale_x_discrete(labels =education_m$label2) + scale_y_continuous(breaks=seq(0,1,0.1))





```

#conservative/liberal


```{r}



d <- select(a,merged,ind,Q7,Q5,Q9,Q88,Q11,Q90_1,Q90_2,Q90_3,Q90_4,Q13,Q85,Q86,Q89,Q87_1,Q87_2,Q87_3,Q87_6,Q87_8,Q87_9)
d <- na.omit(d)



d$ind <- as.factor(d$ind)
d$Q88 <- as.factor(d$Q88)
d$merged2 <-((d$merged-1)/(5-1))
liberal <-  na.omit(select(d,merged2,ind,Q88))

liberal <- liberal %>%
 group_by(ind, Q88) %>%
  summarise(mean = mean(merged2),sd = sd(merged2))

liberal_m <- liberal[-4]
liberal_s <- liberal[-3]

#liberal_m <- melt(liberal_m)
#ggplot(liberal, aes(ind, mean, fill = Q88)) + 
 # geom_bar(stat="identity", position = "dodge")

liberal_m$sd <- liberal_s$sd
liberal_m$n <- as.integer(table(d$Q88,d$ind))


liberal_m$label2 <- c("Most Liked", rep("Least Liked",(length(liberal_m$mean)-1)))

liberal_m$Ideology <- as.factor(rep(c("Extremely liberal","Moderately liberal
", "Slightly liberal","Neither liberal nor conservative","Slightly conservative","Moderately conservative","Extremely conservative"),2))

liberal_m$Ideology<- factor(liberal_m$Ideology, levels =c("Extremely liberal","Moderately liberal
", "Slightly liberal","Neither liberal nor conservative","Slightly conservative","Moderately conservative","Extremely conservative") )

pd = position_dodge(.9)    ### How much to jitter the points on the plot

ggplot(liberal_m,                ### The data frame to use.
       aes(x     = ind,
           y     = mean,
           fill= Ideology)) + 
  geom_bar(stat="identity", position = "dodge")  +

    geom_errorbar(aes(ymin  = mean - 1.96*(sd/sqrt(n)),
                      ymax  = mean + 1.96*(sd/sqrt(n))),
                         size=.5,  
                width=.2,
                      position = pd) +
    

    ylab("Mean Deplatforming Index Value") + xlab("Experimental Groups")  + ggtitle("DI Value between Experimental Groups by Ideological Leaning") +
  theme(plot.title = element_text(hjust = 0.5),panel.background = element_rect(fill = 'beige'), axis.text.x =element_text(colour = "black", face = "bold"))+
  scale_x_discrete(labels =liberal_m$label2) +
  scale_x_discrete(labels =party_m$label2) + scale_y_continuous(breaks=seq(0,1,0.1))


```


#Party


```{r}

d <- select(a,merged,ind,Q7,Q5,Q9,Q88,Q11,Q90_1,Q90_2,Q90_3,Q90_4,Q13,Q85,Q86,Q89,Q87_1,Q87_2,Q87_3,Q87_6,Q87_8,Q87_9)
d <- na.omit(d)



d$ind <- as.factor(d$ind)
d$Q11 <- as.factor(d$Q11)
d$merged2 <-((d$merged-1)/(5-1))
party <-  na.omit(select(d,merged2,ind,Q11))



party <- party %>%
 group_by(ind, Q11) %>%
  summarise(mean = mean(merged2),sd = sd(merged2))

party_m <- party[-4]
party_s <- party[-3]

#party_m <- melt(party_m)
#ggplot(party, aes(ind, mean, fill = Q11)) + 
 # geom_bar(stat="identity", position = "dodge")

party_m$sd <- party_s$sd
party_m$n <- as.integer(table(d$Q11,d$ind))


party_m$label2 <- c("Most Liked", rep("Least Liked",(length(party_m$mean)-1)))

party_m$Party <- as.factor(rep(c("Republican","Democrat
", "Independent","Other"),2))

party_m$Party <- factor(party_m$Party, levels =c("Republican","Democrat
", "Independent","Other") )

pd = position_dodge(.9)    ### How much to jitter the points on the plot

ggplot(party_m,                ### The data frame to use.
       aes(x     = ind,
           y     = mean,
           fill= Party)) + 
  geom_bar(stat="identity", position = "dodge")  +

    geom_errorbar(aes(ymin  = mean - 1.96*(sd/sqrt(n)),
                      ymax  = mean + 1.96*(sd/sqrt(n))),
                         size=.5,  
                width=.2,
                      position = pd) +
    

    ylab("Mean Deplatforming Index Value") + xlab("Experimental Groups")  + ggtitle("Deplatforming Index Value between Experimental Groups by Party") +
  theme(plot.title = element_text(hjust = 0.5),panel.background = element_rect(fill = 'beige'), axis.text.x =element_text(colour = "black", face = "bold"))+
  scale_x_discrete(labels =party_m$label2) + scale_y_continuous(breaks=seq(0,1,0.1))


```

#Activity

```{r}

d <- select(a,merged,ind,Q7,Q5,Q9,Q88,Q11,Q90_1,Q90_2,Q90_3,Q90_4,Q13,Q85,Q86,Q89,Q87_1,Q87_2,Q87_3,Q87_6,Q87_8,Q87_9)
d <- na.omit(d)

d$Q90_1 <- car::recode(d$Q90_1,"c('2') = '0'") 
d$Q90_2 <- car::recode(d$Q90_2,"c('2') = '0'") 
d$Q90_3 <- car::recode(d$Q90_3,"c('2') = '0'") 
d$Q90_4 <- car::recode(d$Q90_4,"c('2') = '0'") 
d$Q90<- d$Q90_1 + d$Q90_4 + d$Q90_3 + d$Q90_2

d$ind <- as.factor(d$ind)
d$Q90 <- as.factor(d$Q90)
d$merged2 <-((d$merged-1)/(5-1))
activity <-  na.omit(select(d,merged2,ind,Q90))

activity <- activity %>%
 group_by(ind, Q90) %>%
  summarise(mean = mean(merged2),sd = sd(merged2))

activity_m <- activity[-4]
activity_s <- activity[-3]

#activity_m <- melt(activity_m)
#ggplot(activity, aes(ind, mean, fill = Q90)) + 
 # geom_bar(stat="identity", position = "dodge")

activity_m$sd <- activity_s$sd
activity_m$n <- as.integer(table(d$Q90,d$ind))


activity_m$label2 <- c("Most Liked", rep("Least Liked",(length(activity_m$mean)-1)))

activity_m$Political_Activity <- as.factor(rep(c("0","1
", "2","3","4"),2))

activity_m$Political_Activity <- factor(activity_m$Political_Activity, levels =c("0","1
", "2","3","4") )

pd = position_dodge(.9)    ### How much to jitter the points on the plot

ggplot(activity_m,                ### The data frame to use.
       aes(x     = ind,
           y     = mean,
           fill= Political_Activity)) + 
  geom_bar(stat="identity", position = "dodge")  +

    geom_errorbar(aes(ymin  = mean - 1.96*(sd/sqrt(n)),
                      ymax  = mean + 1.96*(sd/sqrt(n))),
                         size=.5,  
                width=.2,
                      position = pd) +
    

    ylab("Mean Deplatforming Index Value") + xlab("Experimental Groups")  + ggtitle("Deplatforming Index Value between Experimental Groups by Political Activity") +
  theme(plot.title = element_text(hjust = 0.5),panel.background = element_rect(fill = 'beige'), axis.text.x =element_text(colour = "black", face = "bold"))+
  scale_x_discrete(labels =activity_m$label2) + scale_y_continuous(breaks=seq(0,1,0.1))

```


#Ethnicity

```{r}

d <- select(a,merged,ind,Q7,Q5,Q9,Q88,Q11,Q90_1,Q90_2,Q90_3,Q90_4,Q13,Q85,Q86,Q89,Q87_1,Q87_2,Q87_3,Q87_6,Q87_8,Q87_9)
d <- na.omit(d)


d$ind <- as.factor(d$ind)
d$Q13 <- as.factor(d$Q13)
d$merged2 <-((d$merged-1)/(5-1))
ethnicity <-  na.omit(select(d,merged2,ind,Q13))

ethnicity <- ethnicity %>%
 group_by(ind, Q13) %>%
  summarise(mean = mean(merged2),sd = sd(merged2))

ethnicity_m <- ethnicity[-4]
ethnicity_s <- ethnicity[-3]

#ethnicity_m <- melt(ethnicity_m)
#ggplot(ethnicity, aes(ind, mean, fill = Q13)) + 
 # geom_bar(stat="identity", position = "dodge")

ethnicity_m$sd <- ethnicity_s$sd
ethnicity_m$n <- as.integer(table(d$Q13,d$ind))


ethnicity_m$label2 <- c("Most Liked", rep("Least Liked",(length(ethnicity_m$mean)-1)))

ethnicity_m$Ethnicity <- as.factor(rep(c("White, Non-Hispanic","African American
", "Latino or Hispanic","Asian","Native American", "Two or more","Other/Prefer not to say"),2))

ethnicity_m$Ethnicity <- factor(ethnicity_m$Ethnicity, levels =c("White, Non-Hispanic","African American
", "Latino or Hispanic","Asian","Native American", "Two or more","Other/Prefer not to say") )

pd = position_dodge(.9)    ### How much to jitter the points on the plot

ggplot(ethnicity_m,                ### The data frame to use.
       aes(x     = ind,
           y     = mean,
           fill= Ethnicity)) + 
  geom_bar(stat="identity", position = "dodge")  +

    geom_errorbar(aes(ymin  = mean - 1.96*(sd/sqrt(n)),
                      ymax  = mean + 1.96*(sd/sqrt(n))),
                         size=.5,  
                width=.2,
                      position = pd) +
    

    ylab("Mean Deplatforming Index Value") + xlab("Experimental Groups")  + ggtitle("Deplatforming Index Value between Experimental Groups by Ethnicity") +
  theme(plot.title = element_text(hjust = 0.5),panel.background = element_rect(fill = 'beige'), axis.text.x =element_text(colour = "black", face = "bold"))+
  scale_x_discrete(labels =ethnicity_m$label2) + scale_y_continuous(breaks=seq(0,1,0.1))

```


#religion

```{r}

d <- select(a,merged,ind,Q7,Q5,Q9,Q88,Q11,Q90_1,Q90_2,Q90_3,Q90_4,Q13,Q85,Q86,Q89,Q87_1,Q87_2,Q87_3,Q87_6,Q87_8,Q87_9)
d <- na.omit(d)

d <- d[d$Q85 != 4, ]
d$ind <- as.factor(d$ind)
d$Q85 <- as.factor(d$Q85)
d$merged2 <-d$merged2 <-((d$merged-1)/(5-1))
religion <-  na.omit(select(d,merged2,ind,Q85))

religion <- religion %>%
 group_by(ind, Q85) %>%
  summarise(mean = mean(merged2),sd = sd(merged2))

religion_m <- religion[-4]
religion_s <- religion[-3]

#religion_m <- melt(religion_m)
#ggplot(religion, aes(ind, mean, fill = Q85)) + 
 # geom_bar(stat="identity", position = "dodge")

religion_m$sd <- religion_s$sd
religion_m$n <- as.integer(na.omit(ifelse(as.integer(table(d$Q85,d$ind)) == 0, NA,as.integer(table(d$Q85,d$ind)))))


religion_m$label2 <- c("Most Liked", rep("Least Liked",(length(religion_m$mean)-1)))

religion_m$Religion <- as.factor(rep(c("Buddhism", "Christianity","Hinduism", "Judaism","None","Other"),2))

religion_m$Religion <- factor(religion_m$Religion, levels =c("Buddhism", "Christianity","Hinduism"
, "Judaism","None","Other") )

pd = position_dodge(.9)    ### How much to jitter the points on the plot

ggplot(religion_m,                ### The data frame to use.
       aes(x     = ind,
           y     = mean,
           fill= Religion)) + 
  geom_bar(stat="identity", position = "dodge")  +

    geom_errorbar(aes(ymin  = mean - 1.96*(sd/sqrt(n)),
                      ymax  = mean + 1.96*(sd/sqrt(n))),
                         size=.5,  
                width=.2,
                      position = pd) +
    

    ylab("Mean Deplatforming Index Value") + xlab("Experimental Groups")  + ggtitle("Deplatforming Index Value between Experimental Groups by Religion") +
  theme(plot.title = element_text(hjust = 0.5),panel.background = element_rect(fill = 'beige'), axis.text.x =element_text(colour = "black", face = "bold"))+
  scale_x_discrete(labels =religion_m$label2) + scale_y_continuous(breaks=seq(0,1,0.1))



```


#degree

```{r}

d <- select(a,merged,ind,Q7,Q5,Q9,Q88,Q11,Q90_1,Q90_2,Q90_3,Q90_4,Q13,Q85,Q86,Q89,Q87_1,Q87_2,Q87_3,Q87_6,Q87_8,Q87_9)
d <- na.omit(d)


d$ind <- as.factor(d$ind)
d$Q86 <- as.factor(d$Q86)
d$merged2 <-((d$merged-1)/(5-1))
degree <-  na.omit(select(d,merged2,ind,Q86))

degree <- degree %>%
 group_by(ind, Q86) %>%
  summarise(mean = mean(merged2),sd = sd(merged2))

degree_m <- degree[-4]
degree_s <- degree[-3]

#degree_m <- melt(degree_m)
#ggplot(degree, aes(ind, mean, fill = Q86)) + 
 # geom_bar(stat="identity", position = "dodge")

degree_m$sd <- degree_s$sd
degree_m$n <- as.integer(table(d$Q86,d$ind))


degree_m$label2 <- c("Most Liked", rep("Least Liked",(length(degree_m$mean)-1)))

degree_m$Religiousness <- as.factor(rep(c("Not religious", "Slightly religious","Moderately religious", "Very religious"),2))

degree_m$Religiousness <- factor(degree_m$Religiousness, levels =c("Not religious", "Slightly religious","Moderately religious", "Very religious") )

pd = position_dodge(.9)    ### How much to jitter the points on the plot

ggplot(degree_m,                ### The data frame to use.
       aes(x     = ind,
           y     = mean,
           fill= Religiousness)) + 
  geom_bar(stat="identity", position = "dodge")  +

    geom_errorbar(aes(ymin  = mean - 1.96*(sd/sqrt(n)),
                      ymax  = mean + 1.96*(sd/sqrt(n))),
                         size=.5,  
                width=.2,
                      position = pd) +
    

    ylab("Mean Deplatforming Index Value") + xlab("Experimental Groups")  + ggtitle("DI Value between Experimental Groups by Degree of Religiousness") +
  theme(plot.title = element_text(hjust = 0.5),panel.background = element_rect(fill = 'beige'), axis.text.x =element_text(colour = "black", face = "bold"))+
  scale_x_discrete(labels =degree_m$label2) + scale_y_continuous(breaks=seq(0,1,0.1))
```


